Data Preparation

### 2019-01-15 Data Preparation.Rmd
debug data prep

# Import Data
The datasets we use are saved as spreadsheet on our google drive *DARS* (with exeption of grade data saved as csv files on the computer for privacy reasons). We use the function `gsheet2tbl` to import them to `R Studio` as tibbles. We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.

## Setup
First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`. ` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively). We also any imported emtpy cells.
```{r import list}
lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
lists <- list(
  Assessment      = lists_brut$Assessment,
  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
  )
rm(lists_brut)
```

@@

## Textual Data

### Course Catalogues
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
```{r import corpus_catalogues, cache = TRUE}
corpus_catalogues <- Corpus(x             = DirSource("Catalogues"),
                            readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

@@

## Textual Data

### Extracting Text
In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues, as well as the  *full text*  from the Course Manuals.

@@

dictionary <- select(d_overview, Code, word) %>%
  rbind(d_manual) %>% 
  select(word) %>%
  distinct %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))
# terms for which the stem differs from the original word
filter(dictionary, word != word_stem)
```
Finally, we create a function `stem_with_dictionary` that performs a left join on the dataframe it takes as input with `dictionary`, thus adding the word stems to the original dataframe.

@@

d_description <- stem_with_dictionary(d_description)
d_overview <- stem_with_dictionary(d_overview)
d_manual <- stem_with_dictionary(d_manual)
rm(stem_hunspell, stem_with_dictionary)
print(d_description) # See starting - start
```

### Removing Stopwords
Finally, we want to filter out some uninformative words from our textual data. For this, we first store all the unwanted words in a vector `sw_owm`. We also create function `remove_sw` which receives a dataframe as input and filters out all words in `sw_own`. Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
```{r}
# Own stop words
sw_own <- c("______________________________________________________________________________")
remove_sw <- function(data) data %>%
  filter(! word %in% c(stop_words$word, sw_own))
d_description <- remove_sw(d_description)
d_overview <- remove_sw(d_overview)
d_manual <- remove_sw(d_manual)

@@

##Student Data
(In this section we use: `d_transcript`- contains the transcript information of students as was provided. It has 40 columns, and rows correspond roughly to a type of grade (e.g. final grade, attendance) per student per course per time they took it).

###Selecting Variables

>>>>

# Import Data
The datasets we use are saved as spreadsheet on our google drive *DARS* (with exeption of grade data saved as csv files on the computer for privacy reasons). We use the function `gsheet2tbl` to import them to `R Studio` as tibbles. We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.
## Setup
First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`. ` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively). We also any imported emtpy cells.
```{r import list}
lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
lists <- list(
  Assessment      = lists_brut$Assessment,
  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
  )
rm(lists_brut)
```

@@

## Textual Data
### Course Catalogues
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
```{r import corpus_catalogues, cache = TRUE}
corpus_catalogues <- Corpus(x             = DirSource("Catalogues"),
                            readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

@@

## Textual Data
### Extracting Text
In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues, as well as the  *full text*  from the Course Manuals.

@@

dictionary <- select(d_overview, Code, word) %>%
  rbind(d_manual) %>% 
  distinct(word) %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))

# terms for which the stem differs from the original word
filter(dictionary, word != word_stem)
```
Finally, we create a function `stem_with_dictionary` that performs a left join on the dataframe it takes as input with `dictionary`, thus adding the word stems to the original dataframe.

@@

d_description <- stem_with_dictionary(d_description)
d_overview <- stem_with_dictionary(d_overview)
d_manual <- stem_with_dictionary(d_manual)

rm(stem_hunspell, stem_with_dictionary)
print(d_description) # See starting - start
```

### Removing Stopwords
Finally, we want to filter out some uninformative words from our textual data. For this, we first store all the unwanted words in a vector `sw_owm`. We also create function `remove_sw` which receives a dataframe as input and filters out all words in `sw_own`. Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
```{r}
# Own stop words
sw_own <- c("______________________________________________________________________________")

remove_sw <- function(data) data %>%
  filter(! word %in% c(stop_words$word, sw_own))

d_description <- remove_sw(d_description)
d_overview <- remove_sw(d_overview)
d_manual <- remove_sw(d_manual)

@@

## Student Data
(In this section we use: `d_transcript`- contains the transcript information of students as was provided. It has 40 columns, and rows correspond roughly to a type of grade (e.g. final grade, attendance) per student per course per time they took it).

### Selecting Variables
